---
title: "Pericycle mixed ANOVA"
output:
  html_document:
    toc: true
    df_print: paged
    toc_float:
      collapsed: false
      smooth_scroll: false
  pdf_document: default
  word_document: default
---

  
```{r message=FALSE, warning=FALSE, include=FALSE}
library(xlsx)
library(ggplot2)
library(pheatmap)
library(mixtools)
library(mclust)
library(grid)
library(gridExtra)
library(dplyr)
library(tidyr)
library(knitr)
library(lmerTest)
library(lme4)
library(RColorBrewer)
library(nlme)
library(multcomp)
library(MASS)
library(lattice)
library(EMAtools)
library(sjstats)
library(performance)
library(insight)
```

```{r - data, include=FALSE}
## Reading pericycle data
pericycle<-read.csv("./PeriCycle_cells_ready.csv",stringsAsFactors = F)
## Rmoving  plants with problematic quantification
pericycle<-pericycle[!pericycle$plantID=="X20171217__col.0.1.nM.BL_A",]
pericycle<-pericycle[!pericycle$plantID=="Col_20170717",]
pericycle<-pericycle[!pericycle$plantID=="Bri1_20170802_07",]
pericycle<-pericycle[!pericycle$plantID=="Bri1_20170817",]
# Changing plant ID for consistency with other IDs
pericycle$plantID[pericycle$plantID=="X20171217__col.0.1.nM.BL_B"]<-"Col_BL20171217__col.0.1.nM.BL_B"

pericycle_ColBL1<-read.xlsx("./col_BL_1_updated_20200423.xlsx",sheetName = "Pericycle",stringsAsFactors = F)
pericycle_ColBL1<-pericycle_ColBL1[,c(1:7,9,8)]
pericycle_ColBL2<-read.xlsx("./col_BL_2_updated_20200423.xlsx",sheetName = "Pericycle",stringsAsFactors = F)
pericycle_ColBL2<-pericycle_ColBL2[,c(1:7,9,8)]
#

#Adding Cell ID (X column) correcting colmn order and names
pericycle_ColBL1$X<-paste(pericycle_ColBL1$plant.ID,pericycle_ColBL1$Cell.ID,sep = "_")
pericycle_ColBL1$PlantType<-"colBL"
pericycle_ColBL1<-pericycle_ColBL1[,c(10,11,2,3,4,5,6,7,9,8)]
colnames(pericycle_ColBL1)<-colnames(pericycle)

pericycle_ColBL2$X<-paste(pericycle_ColBL2$plant.ID,pericycle_ColBL2$Cell.ID,sep = "_")
pericycle_ColBL2$PlantType<-"colBL"
pericycle_ColBL2<-pericycle_ColBL2[,c(10,11,2,3,4,5,6,7,9,8)]
colnames(pericycle_ColBL2)<-colnames(pericycle)

pericycle_col_20191029_03<-read.xlsx("./col_20191029_03_new.xlsx",sheetName = "Pericycle",stringsAsFactors = F)
pericycle_col_20191029_03$X<-paste(pericycle_col_20191029_03$plant.ID,pericycle_col_20191029_03$Cell.ID,sep = "_")
pericycle_col_20191029_03$PlantType<-"col"
pericycle_col_20191029_03<-pericycle_col_20191029_03[,c(10,11,2:7,8,9)]
colnames(pericycle_col_20191029_03)<-colnames(pericycle)

pericycle_bri1_20170328_02<-read.xlsx("./bri1_20170328_02_updated.xlsx",sheetName = "Pericycle",stringsAsFactors = F)
pericycle_bri1_20170328_02$X<-paste(pericycle_bri1_20170328_02$plant.ID,pericycle_bri1_20170328_02$Cell.ID,sep = "_")
pericycle_bri1_20170328_02$PlantType<-"bri"
pericycle_bri1_20170328_02<-pericycle_bri1_20170328_02[,c(10,11,2:7,8,9)]
colnames(pericycle_bri1_20170328_02)<-colnames(pericycle)


pericycle1<-rbind(pericycle,pericycle_ColBL1,pericycle_ColBL2,pericycle_col_20191029_03,pericycle_bri1_20170328_02)
pericycle1<-pericycle1[is.finite(pericycle1$length),]
pericycle1<-pericycle1[pericycle1$length!=0,]
pericycle_cells_ready2hm<-pericycle1
pericycle_cells_ready2hm[,c(6,7,8,9,10)]<-log2(pericycle_cells_ready2hm[,c(6,7,8,9,10)])
#Removing unnecessary data frames
rm("pericycle","pericycle_bri1_20170328_02","pericycle_col_20191029_03","pericycle_ColBL2","pericycle_ColBL1")
```

#mixture models with EM algorithm - Separating meristem from elongation zone
```{r - lableling meristem cells, echo=FALSE, message=FALSE, warning=FALSE}
#histograms + em algorithm
plot_mix_comps <- function(x, mu, sigma, lam) {
  lam * dnorm(x, mu, sigma)
}
pericycle_cells_ready2hm$ProbeMeristem<-0
##All

len_col <- pericycle_cells_ready2hm$length[pericycle_cells_ready2hm$PlantType=="col"]
len_Bri <- pericycle_cells_ready2hm$length[pericycle_cells_ready2hm$PlantType=="bri"]
len_colBL <- pericycle_cells_ready2hm$length[pericycle_cells_ready2hm$PlantType=="colBL"]

set.seed(2)
mixmdl <- normalmixEM2comp(len_col, , sigsqrd = c(1,1),mu=c(-1,1),lambda = 0.5)
rdr<-order(mixmdl$mu)
hstem<-data.frame(x = mixmdl$x) %>%
  ggplot() +
  geom_histogram(aes(x, ..density..), binwidth = 0.2, colour = "gray50", 
                 fill = "pink") +
  #geom_density(aes(x, ..density..), bw=0.2, colour = "black",lwd = 1.5)+
  stat_function(geom = "line", fun = plot_mix_comps,
                args = list(mixmdl$mu[rdr[1]], mixmdl$sigma[rdr[1]], lam = mixmdl$lambda[rdr[1]]),
                colour = "blue", lwd = 1) +
  stat_function(geom = "line", fun = plot_mix_comps,
                args = list(mixmdl$mu[rdr[2]], mixmdl$sigma[rdr[2]], lam = mixmdl$lambda[rdr[2]]),
                colour = "red", lwd = 1) +
  ylab("Density")+
  xlab("Length")+
  labs(title = "col")

for_scatter<- data.frame(Distance=pericycle_cells_ready2hm[pericycle_cells_ready2hm$PlantType=="col",5],
                         Length=pericycle_cells_ready2hm[pericycle_cells_ready2hm$PlantType=="col",6],
                         PlantType=pericycle_cells_ready2hm[pericycle_cells_ready2hm$PlantType=="col",2],
                         ProbMeristem=c("red","blue")[1+as.numeric(mixmdl$posterior[,rdr[1]]>0.8)],
                         shape=21)
for_scatter$PlantType<-gsub("col","black",for_scatter$PlantType)


scem<-ggplot(for_scatter, aes(x = Distance, y = Length, color = ProbMeristem,shape=shape)) + 
  geom_point(size=2,stroke=1)+
  scale_color_identity(guide = "legend",labels=c("Meristem","Mature"))+ 
  scale_shape_identity()+
  
  guides(fill = guide_legend(override.aes = list(color =c("black"))),color = guide_legend(override.aes = list(shape =c(1))))
grid.arrange(hstem, scem,ncol = 1)

grid_pericycle_col_MM<-arrangeGrob(hstem, scem,ncol = 1)
ggsave(grid_pericycle_col_MM,filename="grid_pericycle_col_MM_Feb2021.eps",height = 12,width = 14,units = "cm",device=cairo_ps)

##Bri

set.seed(2)
mixmdl_bri <- normalmixEM2comp(len_Bri, , sigsqrd = c(1,1),mu=c(-1,1),lambda = 0.5)
rdr<-order(mixmdl_bri$mu)
hstem<-data.frame(x = mixmdl_bri$x) %>%
  ggplot() +
  geom_histogram(aes(x, ..density..), binwidth = 0.2, colour = "gray50", 
                 fill = "pink") +
  #geom_density(aes(x, ..density..), bw=0.2, colour = "black",lwd = 1.5)+
  stat_function(geom = "line", fun = plot_mix_comps,
                args = list(mixmdl_bri$mu[rdr[1]], mixmdl_bri$sigma[rdr[1]], lam = mixmdl_bri$lambda[rdr[1]]),
                colour = "blue", lwd = 1) +
  stat_function(geom = "line", fun = plot_mix_comps,
                args = list(mixmdl_bri$mu[rdr[2]], mixmdl_bri$sigma[rdr[2]], lam = mixmdl_bri$lambda[rdr[2]]),
                colour = "red", lwd = 1)+
  ylab("Density")+
  xlab("Length")+
  labs(title = "Bri1")
for_scatter<- data.frame(Distance=pericycle_cells_ready2hm[pericycle_cells_ready2hm$PlantType=="bri",5],
                         Length=pericycle_cells_ready2hm[pericycle_cells_ready2hm$PlantType=="bri",6],
                         PlantType=pericycle_cells_ready2hm[pericycle_cells_ready2hm$PlantType=="bri",1],
                         ProbMeristem=c("red","blue")[1+as.numeric(mixmdl_bri$posterior[,rdr[1]]>0.8)],
                         shape=21)

for_scatter$PlantType<-gsub("bri","yellow",for_scatter$PlantType)
#for_scatter$PlantType<-c("black","yellow")[1+as.numeric(for_scatter$PlantType=="bri")]
scem<-ggplot(for_scatter, aes(x = Distance, y = Length, color = ProbMeristem,shape=shape)) + 
  geom_point(size=2,stroke=1)+
  scale_color_identity(guide = "legend",labels=c("Meristem","Mature"))+ 
  scale_shape_identity()+
  
  guides(fill = guide_legend(override.aes = list(color =c("yellow"))),color = guide_legend(override.aes = list(shape =c(1))))

grid.arrange(hstem, scem,ncol = 1)

grid_pericycle_Bri1_MM<-arrangeGrob(hstem, scem,ncol = 1)
ggsave(grid_pericycle_Bri1_MM,filename="grid_pericycle_Bri1_MM_Feb2021.eps",height = 12,width = 14,units = "cm",device=cairo_ps)

##colBL

set.seed(2)
mixmdl_colBL <- normalmixEM2comp(len_colBL, , sigsqrd = c(1,1),mu=c(-1,1),lambda = 0.5)
rdr<-order(mixmdl_colBL$mu)
hstem<-data.frame(x = mixmdl_colBL$x) %>%
  ggplot() +
  geom_histogram(aes(x, ..density..), binwidth = 0.2, colour = "gray50", 
                 fill = "pink") +
  #geom_density(aes(x, ..density..), bw=0.2, colour = "black",lwd = 1.5)+
  stat_function(geom = "line", fun = plot_mix_comps,
                args = list(mixmdl_colBL$mu[rdr[1]], mixmdl_colBL$sigma[rdr[1]], lam = mixmdl_colBL$lambda[rdr[1]]),
                colour = "blue", lwd = 1) +
  stat_function(geom = "line", fun = plot_mix_comps,
                args = list(mixmdl_colBL$mu[rdr[2]], mixmdl_colBL$sigma[rdr[2]], lam = mixmdl_colBL$lambda[rdr[2]]),
                colour = "red", lwd = 1) +
  ylab("Density")+
  xlab("Length")+
  labs(title = "colBL")

for_scatter<- data.frame(Distance=pericycle_cells_ready2hm[pericycle_cells_ready2hm$PlantType=="colBL",5],
                         Length=pericycle_cells_ready2hm[pericycle_cells_ready2hm$PlantType=="colBL",6],
                         PlantType=pericycle_cells_ready2hm[pericycle_cells_ready2hm$PlantType=="colBL",1],
                         ProbMeristem=c("red","blue")[1+as.numeric(mixmdl_colBL$posterior[,rdr[1]]>0.8)],
                         shape=21)

for_scatter$PlantType<-gsub("colBL","yellow",for_scatter$PlantType)
#for_scatter$PlantType<-c("black","yellow")[1+as.numeric(for_scatter$PlantType=="colBL")]
scem<-ggplot(for_scatter, aes(x = Distance, y = Length, color = ProbMeristem,shape=shape)) + 
  geom_point(size=2,stroke=1)+
  scale_color_identity(guide = "legend",labels=c("Meristem","Mature"))+ 
  scale_shape_identity()+
  
  guides(fill = guide_legend(override.aes = list(color =c("yellow"))),color = guide_legend(override.aes = list(shape =c(1))))

grid.arrange(hstem, scem,ncol = 1)

grid_pericycle_colBL_MM<-arrangeGrob(hstem, scem,ncol = 1)
ggsave(grid_pericycle_colBL_MM,filename="grid_pericycle_colBL_MM_Feb2021.eps",height = 12,width = 14,units = "cm",device=cairo_ps)

pericycle_cells_ready2hm$ProbeMeristem[pericycle_cells_ready2hm$PlantType=="col"]<-mixmdl$posterior[,order(mixmdl$mu)[1]]
pericycle_cells_ready2hm$ProbeMeristem[pericycle_cells_ready2hm$PlantType=="bri"]<-mixmdl_bri$posterior[,order(mixmdl_bri$mu)[1]]
pericycle_cells_ready2hm$ProbeMeristem[pericycle_cells_ready2hm$PlantType=="colBL"]<-mixmdl_colBL$posterior[,order(mixmdl_colBL$mu)[1]]

```

# Data transformation
## Distance from QC

```{r - distance transformation, echo=FALSE}
pericycle_meristem_cells<-pericycle1
pericycle_meristem_cells$ProbeMeristem<-pericycle_cells_ready2hm$ProbeMeristem
pericycle_meristem_cells<-pericycle_meristem_cells[pericycle_cells_ready2hm$ProbeMeristem>0.8,]
```

### No transformation

```{r - distance no trnasformation, echo=FALSE}
par(mfrow=c(2,3))
hist(pericycle_meristem_cells$distance_from.QC,20)
plot(aov(distance_from.QC~PlantType,data=pericycle_meristem_cells))
```

### Square root transformation

```{r - distance sqrt transformation, echo=FALSE}
par(mfrow=c(2,3))
hist(sqrt(pericycle_meristem_cells$distance_from.QC),20)
plot(aov(sqrt(distance_from.QC)~PlantType,data=pericycle_meristem_cells))
```

## Length

### No Transformation

```{r - length no transformation, echo=FALSE}
par(mfrow=c(2,3))
hist(pericycle_meristem_cells$length,20)
plot(aov(length~PlantType,data=pericycle_meristem_cells))
```

### Log2 Transformation

```{r - length log2 transformation, echo=FALSE}
par(mfrow=c(2,3))
hist(sqrt(pericycle_meristem_cells$length),20)
plot(aov(log2(length)~PlantType,data=pericycle_meristem_cells))
```

## Width

### No Transformation

```{r - width No transformation, echo=FALSE}

par(mfrow=c(2,3))
hist(pericycle_meristem_cells$width,20)
plot(aov(width~PlantType,data=pericycle_meristem_cells))

```

### Square Transformation

```{r - width square transformation, echo=FALSE}
par(mfrow=c(2,3))
hist(pericycle_meristem_cells$width^2,20)
plot(aov(width^2~PlantType,data=pericycle_meristem_cells))
```

### Square root Transformation

```{r -, echo=FALSE}
par(mfrow=c(2,3))
hist(sqrt(pericycle_meristem_cells$width),20)
plot(aov(width^.5~PlantType,data=pericycle_meristem_cells))
```

## Depth
### No Transformation

```{r - depth transformation, echo=FALSE}

par(mfrow=c(2,3))
hist(pericycle_meristem_cells$depth,20)
plot(aov(depth~PlantType,data=pericycle_meristem_cells))
```

### Log2 transformation

```{r - depth Log2 transformation, echo=FALSE}
par(mfrow=c(2,3))
hist(log2(pericycle_meristem_cells$depth),20)
plot(aov(log2(1+depth)~PlantType,data=pericycle_meristem_cells))
```

## Volume

### No transformation
```{r - volume no transformation, echo=FALSE}

par(mfrow=c(2,3))
hist(pericycle_meristem_cells$volume,20)
plot(aov(volume~PlantType,data=pericycle_meristem_cells))
```

### Cubic root

```{r - volume cubic root, echo=FALSE}
par(mfrow=c(2,3))
hist(pericycle_meristem_cells$volume^(1/3),20)
plot(aov(volume^(1/3)~PlantType,data=pericycle_meristem_cells))
```

### Log2

```{r - volume  log2}
par(mfrow=c(2,3))
hist(log2(pericycle_meristem_cells$volume),20)
plot(aov(log2(volume)~PlantType,data=pericycle_meristem_cells))

```

## Surface
### No transformation

```{r - surface no transformation, echo=FALSE}

par(mfrow=c(2,3))
hist(pericycle_meristem_cells$surface,20)
plot(aov(surface~PlantType,data=pericycle_meristem_cells))
```

### Square root

```{r - surface sqrt, echo=FALSE}
par(mfrow=c(2,3))
hist(sqrt(pericycle_meristem_cells$surface),20)
plot(aov(sqrt(surface)~PlantType,data=pericycle_meristem_cells))
```

### Log2

```{r - surface log2, echo=FALSE}
par(mfrow=c(2,3))
hist(log2(pericycle_meristem_cells$surface),20)
plot(aov(log2(surface)~PlantType,data=pericycle_meristem_cells))
```


## Transformations decissions
### Distance from QC - square root
### length - log2
### depth - 1+log2
### width - No
## volume - ^1/3
## surfce - square root

##Boxplots

### transformed data
```{r boxplots-treatments, echo=FALSE, message=FALSE, warning=FALSE}
pericycle_meristem_cells_No_transformation<-pericycle_meristem_cells
write.csv(pericycle_meristem_cells_No_transformation,"pericycle_meristem_cells_No_transformation.csv",row.names = F)
pericycle_meristem_cells$distance_from.QC<-sqrt(pericycle_meristem_cells$distance_from.QC)
pericycle_meristem_cells$length<-log2(pericycle_meristem_cells$length)
pericycle_meristem_cells$depth<-log2(1+pericycle_meristem_cells$depth)
pericycle_meristem_cells$volume<-pericycle_meristem_cells$volume^(1/3)
pericycle_meristem_cells$surface<-sqrt(pericycle_meristem_cells$surface)

#Boxplots
dst<-ggplot(pericycle_meristem_cells,aes(y=distance_from.QC,x=PlantType,col=PlantType))+geom_boxplot()+ theme(axis.text.x = element_blank(),axis.ticks.x = element_blank())
#ggsave("distance_from_QC.tiff")
lngt<-ggplot(pericycle_meristem_cells,aes(y=length,x=PlantType,col=PlantType))+geom_boxplot()+ theme(axis.text.x = element_blank(),axis.ticks.x = element_blank())
#ggsave("length.tiff")
dpt<-ggplot(pericycle_meristem_cells,aes(y=depth,x=PlantType,col=PlantType))+geom_boxplot()+ theme(axis.text.x = element_blank(),axis.ticks.x = element_blank())
#ggsave("depth.tiff")
wdt<-ggplot(pericycle_meristem_cells,aes(y=width,x=PlantType,col=PlantType))+geom_boxplot()+ theme(axis.text.x = element_blank(),axis.ticks.x = element_blank())
#ggsave("width.tiff")
vlm<-ggplot(pericycle_meristem_cells,aes(y=volume,x=PlantType,col=PlantType))+geom_boxplot()+ theme(axis.text.x = element_blank(),axis.ticks.x = element_blank())
#ggsave("volume.tiff")
sa<-ggplot(pericycle_meristem_cells,aes(y=surface,x=PlantType,col=PlantType))+geom_boxplot()+ theme(axis.text.x = element_blank(),axis.ticks.x = element_blank())
#ggsave("volume.tiff")


grid.arrange(dst, lngt, dpt,wdt,vlm,sa,ncol = 2)

```



## Htpothesis testing

### Distance from QC
```{r hypothesis testing for distance, echo=FALSE, message=FALSE, warning=FALSE}


pericycle_cells_ready2anova<-pericycle_meristem_cells
pericycle_cells_ready2anova$PlantType<-as.factor(pericycle_cells_ready2anova$PlantType)

pericyclePQL <- lme(fixed=distance_from.QC ~ PlantType ,
                 random= ~1 | plantID/X,
                 data = pericycle_cells_ready2anova,
                 method = "ML")
summary(pericyclePQL)$tTable
pericycleTKdist=summary(glht(pericyclePQL,linfct=mcp(PlantType="Tukey")))
pericycleTKdist
```

### Length

```{r hypothesis testing for length, echo=FALSE, message=FALSE, warning=FALSE}
print("Length")

pericycleLMElength <- lmer(length ~ PlantType+distance_from.QC+
                          (1 | plantID),
                        data = pericycle_cells_ready2anova,
                        REML=TRUE)
summary(pericycleLMElength)
#summary(PQLlength)$tTable


pericycleTKlength=summary(glht(pericycleLMElength,linfct=mcp(PlantType="Tukey")))
pericycleTKlength

```

### Width

```{r hypothesis testing for width, echo=FALSE, message=FALSE, warning=FALSE}
print("width")

pericycleLMEwidth <- lmer(width ~ PlantType+distance_from.QC+
                         (1 | plantID),
                       data = pericycle_cells_ready2anova,
                       REML=TRUE)

summary(pericycleLMEwidth)

#summary(PQLwidth)$tTable
pericycleTKwidth=summary(glht(pericycleLMEwidth,linfct=mcp(PlantType="Tukey"),alternative="two.sided"))
pericycleTKwidth
```

### Depth

```{r hypothesis testing for depth, echo=FALSE, message=FALSE, warning=FALSE}
print("depth")

pericycleLMEdepth <- lmer(depth ~ PlantType+distance_from.QC+
                         (1 | plantID),
                       data = pericycle_cells_ready2anova,
                       REML=TRUE)

summary(pericycleLMEdepth)
#summary(PQLdepth)$tTable
pericycleTKdepth=summary(glht(pericycleLMEdepth,linfct=mcp(PlantType="Tukey"),alternative="two.sided"))
pericycleTKdepth

```

### Volume

```{r hypothesis testing for volume, echo=FALSE, message=FALSE, warning=FALSE}
print("volume")

pericycleLMEvolume <- lmer(volume ~ PlantType+distance_from.QC+
                          (1 | plantID),
                        data = pericycle_cells_ready2anova,
                        REML=TRUE)

summary(pericycleLMEvolume)
#summary(PQLvolume)$tTable
pericycleTKvolume=summary(glht(pericycleLMEvolume,linfct=mcp(PlantType="Tukey"),alternative="two.sided"))
pericycleTKvolume

```

### Surface

```{r hypothesis testing for surface, echo=FALSE, message=FALSE, warning=FALSE}
print("surface")

pericycleLMEsurface <- lmer(surface ~ PlantType+distance_from.QC+
                           (1 | plantID),
                         data = pericycle_cells_ready2anova,
                         REML = T)

summary(pericycleLMEsurface)
#summary(PQLsurface)$tTable
pericycleTKsurface=summary(glht(pericycleLMEsurface,linfct=mcp(PlantType="Tukey"),alternative="two.sided"))
pericycleTKsurface
```

### variance proportions

```{r - proportions of variance, echo=FALSE}
pericycle_sumarry_variance<-
  rbind(as.data.frame(get_variance(pericycleLMElength)),
        as.data.frame(get_variance(pericycleLMEdepth)),
        as.data.frame(get_variance(pericycleLMEwidth)),
        as.data.frame(get_variance(pericycleLMEvolume)),
        as.data.frame(get_variance(pericycleLMEsurface))
  )
rownames(pericycle_sumarry_variance)<-c("length","depth","width","volume","surface")
pericycle_sumarry_variance_prop<-pericycle_sumarry_variance[,c(1:3)]/rowSums(pericycle_sumarry_variance[,c(1:3)])
pericycle_sumarry_variance_prop<-round(pericycle_sumarry_variance_prop*100)
colnames(pericycle_sumarry_variance_prop)<-c("Fixed","Random","Residual")

lengthTreatmentProp<-anova(pericycleLMElength)$`Sum Sq`[1]/sum(anova(pericycleLMElength)$`Sum Sq`)
lengthDistanceProp<-anova(pericycleLMElength)$`Sum Sq`[2]/sum(anova(pericycleLMElength)$`Sum Sq`)

depthTreatmentProp<-anova(pericycleLMEdepth)$`Sum Sq`[1]/sum(anova(pericycleLMEdepth)$`Sum Sq`)
depthDistanceProp<-anova(pericycleLMEdepth)$`Sum Sq`[2]/sum(anova(pericycleLMEdepth)$`Sum Sq`)

widthTreatmentProp<-anova(pericycleLMEwidth)$`Sum Sq`[1]/sum(anova(pericycleLMEwidth)$`Sum Sq`)
widthDistanceProp<-anova(pericycleLMEwidth)$`Sum Sq`[2]/sum(anova(pericycleLMEwidth)$`Sum Sq`)

volumeTreatmentProp<-anova(pericycleLMEvolume)$`Sum Sq`[1]/sum(anova(pericycleLMEvolume)$`Sum Sq`)
volumeDistanceProp<-anova(pericycleLMEvolume)$`Sum Sq`[2]/sum(anova(pericycleLMEvolume)$`Sum Sq`)

surfaceTreatmentProp<-anova(pericycleLMEsurface)$`Sum Sq`[1]/sum(anova(pericycleLMEsurface)$`Sum Sq`)
surfaceDistanceProp<-anova(pericycleLMEsurface)$`Sum Sq`[2]/sum(anova(pericycleLMEsurface)$`Sum Sq`)


#pericycle_sumarry_variance_prop$Random<-pericycle_sumarry_variance_prop$Cumulative-pericycle_sumarry_variance_prop$Distance
#pericycle_sumarry_variance_prop<-pericycle_sumarry_variance_prop[,-2]

pericycle_sumarry_variance_prop$Treatment<-NA
pericycle_sumarry_variance_prop$Treatment[1]<-pericycle_sumarry_variance_prop$Fixed[1]*lengthTreatmentProp
pericycle_sumarry_variance_prop$Treatment[2]<-pericycle_sumarry_variance_prop$Fixed[2]*depthTreatmentProp
pericycle_sumarry_variance_prop$Treatment[3]<-pericycle_sumarry_variance_prop$Fixed[3]*widthTreatmentProp
pericycle_sumarry_variance_prop$Treatment[4]<-pericycle_sumarry_variance_prop$Fixed[4]*volumeTreatmentProp
pericycle_sumarry_variance_prop$Treatment[5]<-pericycle_sumarry_variance_prop$Fixed[5]*surfaceTreatmentProp


pericycle_sumarry_variance_prop$Distance<-NA
pericycle_sumarry_variance_prop$Distance[1]<-pericycle_sumarry_variance_prop$Fixed[1]*lengthDistanceProp
pericycle_sumarry_variance_prop$Distance[2]<-pericycle_sumarry_variance_prop$Fixed[2]*depthDistanceProp
pericycle_sumarry_variance_prop$Distance[3]<-pericycle_sumarry_variance_prop$Fixed[3]*widthDistanceProp
pericycle_sumarry_variance_prop$Distance[4]<-pericycle_sumarry_variance_prop$Fixed[4]*volumeDistanceProp
pericycle_sumarry_variance_prop$Distance[5]<-pericycle_sumarry_variance_prop$Fixed[5]*surfaceDistanceProp

pericycle_sumarry_variance_prop$id=rownames(pericycle_sumarry_variance_prop)
pericycle_sumarry_variance_prop<-pericycle_sumarry_variance_prop[,-1]
colnames(pericycle_sumarry_variance_prop)[1:2]<-c("Plant","Residual")

pericycle_sumarry_variance_prop<-data.table::melt(pericycle_sumarry_variance_prop,id.vars="id")
pericycle_variance_stacked<-ggplot(pericycle_sumarry_variance_prop,aes(x=id,y=value,fill=variable))+geom_bar(position="stack", stat="identity")
pericycle_variance_stacked

```


```{r}
sessionInfo()
```